---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


**NOTE: This is a practise R package for learning purposes and covers the required steps for `Assignment B2` for partial fulfilment [STAT545B](https://github.com/stat545ubc-2021).**


# summaryTable

<!-- badges: start -->
<!-- badges: end -->

The aim of this package is to provide useful functions to make it easier to produce multiple summary statistics for your datasets, simultaneously.

Currently it just includes the `summary_function()` which outputs a table of the minimum and maximum values, mean and standard deviation. This will be expanded in future assignments for [STAT545B](https://stat545.stat.ubc.ca/course/).


## Installation

You can install the development version of summaryTable from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2021/summaryTable")
```

## Usage

Often when looking at large datasets with multiple conditions or categories, it can be difficult to visualise patterns. This package helps by outputting a useful summary table of important statistics, through the use of a simple function called `summary_function()`.

The function outputs the minimum and maximum values, the mean and the standard deviation for a numerical variable **y** of interest as grouped by a categorical variable or condition **cat**.

The following is a basic example which uses the gapminder dataset package to show how to generate a summary. The code below will generate an output summary of the minimum and maximum values, mean and standard deviation for life expectancy variable **lifeExp** by the country variable **country**:


```{r example}
library(summaryTable)
library(gapminder)
Summary_function(gapminder, country, lifeExp)
```

