---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


**NOTE: This is a practise R package for learning purposes and covers the required steps for `Assignment B2` for partial fulfilment [STAT545B](https://github.com/stat545ubc-2021).**


# summaryTable

<!-- badges: start -->
<!-- badges: end -->

The aim of this package is to provide useful functions to make it easier to produce simple statistics for your datasets.

Currently it just includes the summary_function() which outputs a table of the minimum and maximum values, mean and standard deviation.


## Installation

You can install the development version of summaryTable from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jennybc/regexcite")
```

## Example


Often when looking at large datasets with multiple conditions or categories, it can be difficult to visualise patterns. This package helps by outputting a summary table for a ***numerical variable*** as grouped by a condition. 

Below is a basic example which shows you how to generate a common problem:

```{r example}
library(summaryTable)
## basic example code
```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

